QPLIB: A Library of Quadratic Programming Instances

### 2018-02-03 methods.tex
Update methods.tex

\textcolor{red}{We refer the interested reader to 
\cite{book:2077007} and 
\cite{Michae-2007}\todo{was it really mean to cite the book review instead of the book here?}\ for further details on the solution methods.}

@@

Nearly all of the complete solvers in Table \ref{t:solvers} that address $\mathcal{NP}$-hard problems (i.e.~those in \textit{QGQ}$\smallsetminus$\textit{CCC}) are based on Branch-and-Bound (BB) \cite{land_doig}. When the BB algorithm is allowed to branch on coordinate directions corresponding to continuous variables, it is called \emph{spatial} BB (sBB) \cite{dakin,couenne}. BB algorithms are\todo{require?}\ exponential time in the worst case, and their exponential behavior unfortunately often shows up in practice. They can also be used heuristically (forsaking their completeness guarantee) in a number of ways, e.g.~by terminating them early. The following solvers from Table \ref{t:solvers} implement complete BB algorithms for \textit{QGQ} or some subclasses: 
%
\begin{itemize}
 \item \antigone, \baron, \couenne, \lindo, \scip for \textit{QGQ};
 %
\item \cplex for \textit{QGL} and \textit{CGC};
%
 \item \knitro, \bonmin, \sbb, \xpress, \gurobi, and \mosek for \textit{CGC}.
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for \textit{QGQ}. We also note that \lgo implements an incomplete BB algorithm for \textit{QCQ} by using bounds obtained from sampling.

>>>>

\textcolor{red}{We refer the interested reader to 
\cite{book:2077007} and 
\cite{lee2006quadratic} for further details on the solution methods.}

@@

Nearly all of the complete solvers in Table \ref{t:solvers} that address $\mathcal{NP}$-hard problems (i.e.~those in \textit{QGQ}$\smallsetminus$\textit{CCC}) are based on Branch-and-Bound (BB) \cite{land_doig}. When the BB algorithm is allowed to branch on coordinate directions corresponding to continuous variables, it is called \emph{spatial} BB (sBB) \cite{dakin,couenne}. BB algorithms require exponential time in the worst case, and their exponential behavior unfortunately often shows up in practice. They can also be used heuristically (forsaking their completeness guarantee) in a number of ways, e.g.~by terminating them early. The following solvers from Table \ref{t:solvers} implement complete BB algorithms for \textit{QGQ} or some subclasses: 
%
\begin{itemize}
 \item \antigone, \baron, \couenne, \lindo, \scip for \textit{QGQ};
 %
\item \cplex for \textit{QGL} and \textit{CGC};
%
 \item \knitro, \bonmin, \sbb, \xpress, \gurobi, and \mosek for \textit{CGC}.
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for \textit{QGQ}. We also note that \lgo implements an incomplete BB algorithm for \textit{QCQ} by using bounds obtained from sampling.
